XXXXX

### 2014-09-26 paper/paper1.tex
R-44-PATTERN-MATCHING-ON-RDF-LITERALS

@@

\begin{itemize}
	\item R-45-RANGES-OF-RDF-LITERAL-VALUES
  \item R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES
	\item R-46-CONSTRAINING-FACETS
	\item R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS
\end{itemize}

>>>>

\subsubsection{R-44-PATTERN-MATCHING-ON-RDF-LITERALS}

constraints (OWL 2 DL) [description logics abstract syntax]:

\begin{ex}
ToDO
\end{ex}

constraints (OWL 2 DL) [functional-style syntax]:

\begin{ex}
Declaration( Datatype( :SSN ) ) 
DatatypeDefinition( 
    :SSN
    DatatypeRestriction( xsd:string xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ) )     
DataPropertyRange( :hasSSN :SSN ) 
\end{ex}

constraints (OWL 2 DL) [turtle syntax]:

\begin{ex}
:SSN 
    a rdfs:Datatype ;
    owl:equivalentClass [
        a rdfs:Datatype ;
        owl:onDatatype xsd:string ;
        owl:withRestrictions ( 
            [ xsd:pattern "[0-9]{3}-[0-9]{2}-[0-9]{4}" ] ) ] .
\end{ex}

\begin{itemize}
	\item OWL 2 construct 'DatatypeRestriction' not allowed for OWL 2 QL
\end{itemize}

valida data (OWL 2 DL):

\begin{ex}
:IimBernersLee
    :hasSSN "123-45-6789"^^:SSN .
\end{ex}

invalida data (OWL 2 DL):

\begin{ex}
:IimBernersLee
    :hasSSN "123456789"^^:SSN .
\end{ex}

@@

\begin{itemize}
	\item R-44-PATTERN-MATCHING-ON-RDF-LITERALS
	\item R-45-RANGES-OF-RDF-LITERAL-VALUES
	\item R-46-CONSTRAINING-FACETS
	\item R-50-WHITESPACE-HANDLING-OF-RDF-LITERALS
	\item R-142-NEGATIVE-RANGES-OF-RDF-LITERAL-VALUES
\end{itemize}
